---
title: "amarettoTools -- working with AMARETTO outputs"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{amarettoTools -- working with AMARETTO outputs}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Introduction

```{r setup,echo=FALSE,results="hide"}
library(BiocStyle)
library(amarettoTools)
```

AMARETTO is an integrative algorithm for identifying
driver genes in multiomic cancer studies.  In this
package we address the structure of AMARETTO results.

# An illustration in glioblastoma

The main result is a collection of modules of
coexpressed and coregulated genes.  The structure
of the collection can be captured in a graphNEL instance
as defined in the Bioconductor graph package.

```{r lklk}
library(amarettoTools)
data(regulGBM)
regulGBM
# how many modules
length(grep("Module", nodes(regulGBM)))
# target genes in Module_1
adj(regulGBM, "Module_1")
# regulators of Module_1
inEdges("Module_1", regulGBM)
# weights for regulators of module 1
m1regs = inEdges("Module_1", regulGBM)[[1]]
t(t(sapply(edgeWeights(regulGBM, m1regs), "[", "Module_1")))
```

# Conclusions

This graph losslessly collects the relationship information
in the AMARETTO run.  The expression data are propagated
but as far as I can tell, they are just the expression
quantifications from firehose?  So they should not be
propagated but queried from the original source.


